Equations & R Code

### 2017-03-11 manuscript/coexistence-stability_ms.Rmd
more discussion writing

\noindent \textbf{Number of Words in Abstract}: \textcolor{red}{UPDATE}

\noindent \textbf{Number of Words in Main Text}: \textcolor{red}{UPDATE}

\noindent \textbf{Number of References}: \textcolor{red}{UPDATE}

@@

\new{One limitation of our model is that we did not include demographic stochasticity, which can lead to stochastic extinction for small populations as environmental  variability increases} [@Boyce1992].
\new{Previous work has shown how demographic stochasticity and coexistence mechanisms can interact to create a "humped-shape" relationship between coexistence time and environmental variability} [@Adler2008].
\new{This occurs because environmental variability increases coexistence strength and the probability of stochastic extinction simultaneously.
We did not consider this potential effect here because our focus was on large populations that would most influence ecosystem functioning.
However, an interesting extension of our work will be to investigate the role of small populations and demographic stochasticity.}

@@

>>>>

\noindent \textbf{Number of Words in Abstract}: xxx

\noindent \textbf{Number of Words in Main Text}: xxxx

\noindent \textbf{Number of References}: xx

@@

<!---
\new{One limitation of our model is that we did not include demographic stochasticity, which can lead to stochastic extinction for small populations as environmental  variability increases} [@Boyce1992].
\new{Previous work has shown how demographic stochasticity and coexistence mechanisms can interact to create a "humped-shape" relationship between coexistence time and environmental variability} [@Adler2008].
\new{This occurs because environmental variability increases coexistence strength and the probability of stochastic extinction simultaneously.
We did not consider this potential effect here because our focus was on large populations that would most influence ecosystem functioning.
However, an interesting extension of our work will be to investigate the role of small populations and demographic stochasticity.}
--->

@@

LIMITATIONS AND CONCLUSIONS
---------------------------
\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-dependent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability} [see @Thibaut2013 for a review].
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

\new{For example, we assumed all species pairs have the same environmental response correlations (e.g., $\rho_{ij} = \rho$), which is clearly not true in nature and can mediate the impact of dominant species on ecosystem variability} [@Thibaut2013].
\new{We also limited our analysis to four-species communities so we could easily compare the storage effect and relative nonlinearity.
Although our initial results suggest more species rich communities continue to buffer ecosystem variability under the storage effect (Fig. S1-x), future research should focus specifically on the storage effect to elaborate on our initial findings.
Lastly, we ignored demographic stochasticity, assuming our species had a generous seed source that allowed it to bounce back from low population densities.
But this need not be the case, and increasing environmental variability may threaten small populations} [@Boyce1992] \new{even as it promotes coexistence of new species} [@Adler2008].
\new{This dynamic may be especially relevant to applied work because habitat fragmentation and increasing environmental variability are likely to happen together.}

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} @Thibaut2013 \new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}
\new{Likewise, recent advances on quantifying the storage effect in natural communities} [@Ellner2016] \new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}

### 2017-03-11 manuscript/coexistence-stability_ms.tex
more discussion writing

\new{One limitation of our model is that we did not include demographic stochasticity, which can lead to stochastic extinction for small populations as environmental  variability increases}
(Boyce 1992).
\new{Previous work has shown how demographic stochasticity and coexistence mechanisms can interact to create a "humped-shape" relationship between coexistence time and environmental variability}
(Adler \& Drake 2008).
\new{This occurs because environmental variability increases coexistence strength and the probability of stochastic extinction simultaneously.
We did not consider this potential effect here because our focus was on large populations that would most influence ecosystem functioning.
However, an interesting extension of our work will be to investigate the role of small populations and demographic stochasticity.}

@@

@@

>>>>

@@

\subsection{LIMITATIONS AND
CONCLUSIONS}\label{limitations-and-conclusions}

\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-dependent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability}
(see Thibaut \& Connolly 2013 for a review).
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

\new{For example, we assumed all species pairs have the same environmental response correlations (e.g., $\rho_{ij} = \rho$), which is clearly not true in nature and can mediate the impact of dominant species on ecosystem variability}
(Thibaut \& Connolly 2013).
\new{We also limited our analysis to four-species communities so we could easily compare the storage effect and relative nonlinearity.
Although our initial results suggest more species rich communities continue to buffer ecosystem variability under the storage effect (Fig. S1-x), future research should focus specifically on the storage effect to elaborate on our initial findings.
Lastly, we ignored demographic stochasticity, assuming our species had a generous seed source that allowed it to bounce back from low population densities.
But this need not be the case, and increasing environmental variability may threaten small populations}
(Boyce 1992) \new{even as it promotes coexistence of new species} (Adler
\& Drake 2008).
\new{This dynamic may be especially relevant to applied work because habitat fragmentation and increasing environmental variability are likely to happen together.}

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} Thibaut \& Connolly (2013)
\new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}
\new{Likewise, recent advances on quantifying the storage effect in natural communities}
(Ellner et al. 2016)
\new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}

@@

\hypertarget{ref-Ellner2016}{}
Ellner, S.P., Snyder, R.E. \& Adler, P.B. (2016). How to quantify the
temporal storage effect using simulations instead of math. \emph{Ecology
Letters}, 19, 1333--1342.
